Measuring Perceptions and Preferences for Meritocracy

### 2020-12-18 docs/paper.Rmd
update validez convergente

# Conclusion

>>>>

## Reliability and validity analyses

We performed two further analyses in order to add evidence regarding the reliability and validity of the scale. Firstly we test the stability of the scale scores along time through longitudinal measurement invariance methods, and secondly we analyze the convergent validity by assessing the association of the merit scale with related concepts and correspondent measurements.

### Longitudinal measurement invariance

### Convergent validity

_Data_

For this analysis we examined information of the third wave of the study, which included additional measures that allow testing the correlations of the merit scale with some related constructs as opportunity beliefs and personal wherewithal. After listwise deletion of missing cases in socio-demographics information, a total of 1422 individuals took part in the third wave: 668 (46.97%) women and 754 (53.03%) men. The ages of 50.57% of them are 45 years or older, and 36.28% held a tertiary degree.1

_Intruments_

The following scales were included for testing their correlation with the the 8-item meritocracy scale:

- Opportunity beliefs: We used two items of the social inequality module of the International Social Survey Programme. Studies use generally both indicators to measure meritocratic and non-meritocratic beliefs (McCall et al., 2017; Mijs, 2019).  One item measures the importance of individual factors in determining life outcomes by asking for the importance of hard work for getting ahead in life (M=3.76, SD=0.93). The second item asks for the importance of coming from a wealthy family and captures the importance of structural factors in getting ahead (M=2.75, SD=1.27). Participants responded to each item using a 1 (not at all important) to 5 (essential) response scale.

- Personal wherewithal: the questionnaire included The Neoliberal Beliefs Inventory (NBI), which consider four factors: [completar] (Bay-Cheng et al., 2015). We used the factor personal wherewithal that reflects meritocracy beliefs in terms of the importance of personal attributes as strength and skills to yield success. The construct consists of 8 items (e.g., “Any goal can be achieved with enough hard work and talent”, “I’ve benefited from working hard, so there’s no reason others can’t”, “Anyone who is willing to work hard can be succesful in Chile”). Participants answered the items using a 1 (totally disagree) to 6 (totally agree) scale. We simple computed mean scores [reportar alfa the cronbach], with higher scores indicating stronger support for meritocracy (M=3.32, SD=0.89, =0.89).

Both instruments cover mainly the perceptual side of the concept. Therefore, in general we expect larger correlation with meritocratic perceptions than with preferences. In the case of opportunity beliefs, the hard work item should correlate positively with meritocratic perception whereas the importance for coming from a wealthy family is expected to correlate positively with non-meritocratic perceptions. Regarding the second instrument of personal wherewithal, we also anticipate a positive correlation with meritocratic perception and low to null correlations with the other dimensions of the merit scale.

_Results_

We used polyserial correlations to evaluate relationships of meritocractic and non-meritocratic preferences and perceptions with the items of the opportunity beliefs battery. For personal wherewithal,  we examined Pearson correlations.

Table XX about here.

Table X shows ... [completar ]. The findings provide evidence for convergent validity for meritocratic perceptions [re-escribir en el orden de los instrumentos ].
As expected, we see a substantial positive correlation for the association between meritocratic perception and personal wherewithal. Finding for the association of non-meritocratic perception and non-meritocratic item of opportunity beliefs battery is also consistent with our expectation, insofar as the size of the correlation is relevant and the direction of it is positive. For the rest of correlations, we note weak correlations but most directions are consistent with our expectations. One exception is personal wherewithal, with a positive association for this construct. Correlations for meritocratic preference are also weak.

Table XX. Correlations

[insertar tabla imagen o markdown]

Coming from a wealthy family
Hard work
Personal wherewithal
Meritocratic
Perception
-0,1975
0,1877
0,3921
Unmeritocratic
Perception
0,3547
-0,0775
-0,1844
Meritocratic
Preferences
0,1078
0,0779
0,0819
Unmeritocratic
Preferences
-0,0397
0,0824
0,2082

# Conclusions
